---
title: "Kirby Algorithm Test"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(reshape2)
kirby<-read.csv("/Users/bryanxwu/Desktop/bryanxwu/Documents/Extra_Curricular/Research/Poldrack Lab/Practice/R-Practice-/Kirby/kirby.csv")
```


## Data Setup

Here, I will generate the correct parameter values as estimated using the algorithm developed by Gray et al. (2016)

#### Creating Rewards
```{r}

# subset and ignore NA's

kirby.algorithm<-subset(kirby,is.na(kirby$small_amt)==FALSE)
  

# create reward groups
kirby.algorithm$reward<-ifelse((kirby.algorithm$large_amt>=75 & kirby.algorithm$large_amt<=85),3,
                               ifelse((kirby.algorithm$large_amt>=50 & kirby.algorithm$large_amt<=60),2,1))



# check frequencies 
with(kirby.algorithm,table(worker_id,reward))

# identify reward sizes 

small<-unique(kirby.algorithm$trial_index[kirby.algorithm$reward==1])
# 7 9 11 15 17 22 24 26 30

medium<-unique(kirby.algorithm$trial_index[kirby.algorithm$reward==2])

# 5 10 12 14 18 20 25 28 31

large<-unique(kirby.algorithm$trial_index[kirby.algorithm$reward==3])

# 6 8 13 16 19 21 23 27 29 

```

#### Coding discount rate 
```{r}
kirby.algorithm$kvalue[(kirby.algorithm$small_amt==34 & kirby.algorithm$large_amt==35)|(kirby.algorithm$small_amt==54 & kirby.algorithm$large_amt==55)|(kirby.algorithm$small_amt==78&kirby.algorithm$large_amt==80)]<-0.00016

kirby.algorithm$kvalue[(kirby.algorithm$small_amt==28 & kirby.algorithm$large_amt==30)|(kirby.algorithm$small_amt==47 & kirby.algorithm$large_amt==50)|(kirby.algorithm$small_amt==80 & kirby.algorithm$large_amt==85)]<-0.00040

kirby.algorithm$kvalue[(kirby.algorithm$small_amt==22 & kirby.algorithm$large_amt==25)|(kirby.algorithm$small_amt==54 & kirby.algorithm$large_amt==60)|(kirby.algorithm$small_amt==67 &kirby.algorithm$large_amt==75)]<-0.0010

kirby.algorithm$kvalue[(kirby.algorithm$small_amt==25 & kirby.algorithm$large_amt==30)|(kirby.algorithm$small_amt==49 & kirby.algorithm$large_amt==60)|(kirby.algorithm$small_amt==69&kirby.algorithm$large_amt==85)]<-0.0025

kirby.algorithm$kvalue[(kirby.algorithm$small_amt==19 & kirby.algorithm$large_amt==25)|(kirby.algorithm$small_amt==40& kirby.algorithm$large_amt==55)|(kirby.algorithm$small_amt==55&kirby.algorithm$large_amt==75)]<-0.0060

kirby.algorithm$kvalue[(kirby.algorithm$small_amt==24 & kirby.algorithm$large_amt==35)|(kirby.algorithm$small_amt==34 & kirby.algorithm$large_amt==50)|(kirby.algorithm$small_amt==54&kirby.algorithm$large_amt==80)]<-0.016

kirby.algorithm$kvalue[(kirby.algorithm$small_amt==14 & kirby.algorithm$large_amt==25)|(kirby.algorithm$small_amt==27 & kirby.algorithm$large_amt==50)|(kirby.algorithm$small_amt==41&kirby.algorithm$large_amt==75)]<-0.041

kirby.algorithm$kvalue[(kirby.algorithm$small_amt==15 & kirby.algorithm$large_amt==35)|(kirby.algorithm$small_amt==25 & kirby.algorithm$large_amt==60)|(kirby.algorithm$small_amt==33&kirby.algorithm$large_amt==80)]<-0.10

kirby.algorithm$kvalue[(kirby.algorithm$small_amt==11 & kirby.algorithm$large_amt==30)|(kirby.algorithm$small_amt==20 & kirby.algorithm$large_amt==55)|(kirby.algorithm$small_amt==31&kirby.algorithm$large_amt==85)]<-0.25

# I am only hard coding here because I want to fit the data to match the kirby 2009 paper. In the future, I will make sure to use the hyperbolic function and round 



kirby.algorithm$key_press<-ifelse(kirby.algorithm$key_press==80, 2, 1)
# smaller, sooner is 1 and larger, later is 2

```

#### Estimating Parameters 
``` {r}

# reshape

kirby.algorithm<-dcast(kirby.algorithm, worker_id~trial_index, value.var="key_press")
colnames(kirby.algorithm)[2:28]<-paste("MCQ", colnames(kirby.algorithm[,c(2:28)]), sep=".")


# load lookup tables
lookup1 <- read.table("/Users/bryanxwu/Desktop/bryanxwu/Documents/Extra_Curricular/Research/Poldrack Lab/Practice/R-Practice-/Kirby/MCQ_Syntax/lookup1MCQ.txt", header = TRUE)
lookup2 <- read.table("/Users/bryanxwu/Desktop/bryanxwu/Documents/Extra_Curricular/Research/Poldrack Lab/Practice/R-Practice-/Kirby/MCQ_Syntax/lookup2MCQ.txt", header = TRUE)
lookup3 <- read.table("/Users/bryanxwu/Desktop/bryanxwu/Documents/Extra_Curricular/Research/Poldrack Lab/Practice/R-Practice-/Kirby/MCQ_Syntax/lookup3MCQ.txt", header = TRUE)

#Calculate unique value for each sequence of responses


# 7 9 11 15 17 22 24 26 30
kirby.algorithm$MCQ.7 <- kirby.algorithm$MCQ.7*1
kirby.algorithm$MCQ.9 <- kirby.algorithm$MCQ.9*2
kirby.algorithm$MCQ.11 <- kirby.algorithm$MCQ.11*4
kirby.algorithm$MCQ.15 <- kirby.algorithm$MCQ.15*8
kirby.algorithm$MCQ.17 <- kirby.algorithm$MCQ.17*16
kirby.algorithm$MCQ.22 <- kirby.algorithm$MCQ.22*32
kirby.algorithm$MCQ.24 <- kirby.algorithm$MCQ.24*64
kirby.algorithm$MCQ.26 <- kirby.algorithm$MCQ.26*128
kirby.algorithm$MCQ.30 <- kirby.algorithm$MCQ.30*256
kirby.algorithm$SmlSeq <- with (kirby.algorithm, MCQ.7+ MCQ.9+MCQ.11+MCQ.15+MCQ.17+ MCQ.22+MCQ.24+MCQ.26+MCQ.30-510)

# 5 10 12 14 18 20 25 28 31
kirby.algorithm$MCQ.5 <- kirby.algorithm$MCQ.5*1
kirby.algorithm$MCQ.10 <- kirby.algorithm$MCQ.10*2
kirby.algorithm$MCQ.12 <- kirby.algorithm$MCQ.12*4
kirby.algorithm$MCQ.14 <- kirby.algorithm$MCQ.14*8
kirby.algorithm$MCQ.18 <- kirby.algorithm$MCQ.18*16
kirby.algorithm$MCQ.20 <- kirby.algorithm$MCQ.20*32
kirby.algorithm$MCQ.25 <- kirby.algorithm$MCQ.25*64
kirby.algorithm$MCQ.28 <- kirby.algorithm$MCQ.28*128
kirby.algorithm$MCQ.31 <- kirby.algorithm$MCQ.31*256
kirby.algorithm$MedSeq <- with (kirby.algorithm, MCQ.5+ MCQ.10+MCQ.12+MCQ.14+MCQ.18+ MCQ.20+MCQ.25+MCQ.28+MCQ.31-510)

# 6 8 13 16 19 21 23 27 29 

kirby.algorithm$MCQ.6 <- kirby.algorithm$MCQ.6*1
kirby.algorithm$MCQ.8 <- kirby.algorithm$MCQ.8*2
kirby.algorithm$MCQ.13 <- kirby.algorithm$MCQ.13*4
kirby.algorithm$MCQ.16 <- kirby.algorithm$MCQ.16*8
kirby.algorithm$MCQ.19 <- kirby.algorithm$MCQ.19*16
kirby.algorithm$MCQ.21 <- kirby.algorithm$MCQ.21*32
kirby.algorithm$MCQ.23 <- kirby.algorithm$MCQ.23*64
kirby.algorithm$MCQ.27 <- kirby.algorithm$MCQ.27*128
kirby.algorithm$MCQ.29 <- kirby.algorithm$MCQ.29*256
kirby.algorithm$LrgSeq <- with (kirby.algorithm, MCQ.6+ MCQ.8+MCQ.13+MCQ.16+MCQ.19+ MCQ.21+MCQ.23+MCQ.27+MCQ.29-510)

#Remove unwanted columns
kirby.algorithm[2:28] <- list(NULL)



#Merge in MCQindices from lookup table
kirby.algorithm <- (merge(lookup1, kirby.algorithm, by = 'SmlSeq'))
kirby.algorithm <- (merge(lookup2, kirby.algorithm, by = 'MedSeq'))
kirby.algorithm <- (merge(lookup3, kirby.algorithm, by = 'LrgSeq'))


#Return to the original order of rows
kirby.algorithm <- kirby.algorithm[order(kirby.algorithm$worker_id),]
head(kirby.algorithm)

#Arrange columns in ideal order
kirby.algorithm <- kirby.algorithm[c(13,9,10,11,12,5,6,7,8,1,2,3,4)]

#Save MCQ indices to a text file

consistency.algorithm<-arrange(melt(kirby.algorithm, id.vars=c("worker_id"), measure.vars=c("SmlCons", "MedCons", "LrgCons"),variable.name=c("reward"), value.name="consistency",worker_id))[,3]
kirby.algorithm<-cbind(arrange(melt(kirby.algorithm, id.vars=c("worker_id"), measure.vars=c("SmlK", "MedK", "LrgK"), variable.name=c("reward"), value.name="parameter.algorithm",worker_id)), consistency.algorithm)



write.table(kirby.algorithm, file="/Users/bryanxwu/Desktop/bryanxwu/Documents/Extra_Curricular/Research/Poldrack Lab/Practice/R-Practice-/Kirby/MCQ_Syntax/MCQindices.txt", row.names=FALSE)
```
I believe what is going on in this algorithm is that every trial is multiplied by a certain factor so that each magnitude is given a "unique sequece number." Then, predefined k values found on each lookup table (for each reward magnitude) matched to each participant based on the calculated response pattern 
